# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

```{r nice-image, echo=FALSE}
knitr::include_graphics("images/Test_svg.svg", auto_pdf = TRUE)
```

## Testing htmlwidgets

```{r echo=FALSE}
library(ggplot2)
library(plotly)
p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "dodge")
ggplotly(p)
```


```{r echo=FALSE, screenshot.alt="images/ytscreen.png", fig.cap="this is a great link to a [youtube video](https://www.youtube.com/xkLAhU74f3s)"}
knitr::include_url("https://www.youtube.com/embed/xkLAhU74f3s")
```


::: {.theoreme}
La première loi de Newton dit que dans un référentiel galiléen, un système isolé suit un MRU.
:::